\cvsection{Experience}
\begin{cventries}
  \cventry
    {Engineering Manager}
    {OSARO}
    {San Francisco, CA}
    {Nov. 2022 - Present}
    {
      \begin{cvitems}
        \item {Managed a team of up to eight engineers, aligning product requirements with technical solutions using Agile methodology.}
        \item {Led the migration of a Python repository with over 40,000 commits to Rust, coaching developers through the conversion.}
        \item {Oversaw, wrote or reviewed all engineering tasks to deploy production ready computer vision and robotic pick and place solutions.}
      \end{cvitems}
    }
  \cventry
    {Senior Software Engineer}
    {OSARO}
    {San Francisco, CA}
    {Sep. 2019 - Present}
    {
      \begin{cvitems}
        \item {Architected internal and external APIs for deployment of three different products across four continents.}
        \item {Led a cross-functional scrum team working on robotics and ML model accuracy to improve bin clear rate to upwards of 99\% }
        \item {Optimized Python software, model inference, and path planning to increase robotic picking rate to over 1200 picks per hour.}
      \end{cvitems}
    }
  \cventry
    {Science and Engineering Associate}
    {SLAC National Accelerator Laboratory}
    {Menlo Park, CA}
    {Jun. 2015 - Aug. 2019}
    {
      \begin{cvitems}
	     \item {Incorporated a wide variety of instrumentation into the distributed software infrastructure of the accelerator.}
         \item {Led interdisciplinary teams that automated scientific and engineering processes within the lab.}
         \item {Developed a novel UI to display high rate instrument data interfaces for vital scientific operations.}
	     \item {Modernized the Python ecosystem to incorporate test driven development practices and continuous integration.}
      \end{cvitems}
    }
  \cventry
    {Undergraduate Researcher, Astrophysics Department}
    {Astrophysics Department at UCSC}
    {Santa Cruz, CA}
    {July 2014 - Aug 2015}
    {
      \begin{cvitems}
        \item {Developed a Python library that predicted the temporal variance in the spectrum of light emitted by young stellar populations.}
        \item {Optimized scientific algorithms using NumPy and MultiProcessing to improve cycle time of large scale simulations.}
        \item {Contributed to a scientific publication that continued work from my thesis.}
      \end{cvitems}
      }
\end{cventries}
